\input{cv_formatting.tex}
\usepackage{wasysym}

%%%%%%%%%%%%%%%%%%%%%%%%% Begin CV Document %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

\makeheading{Florencia Grattarola -- Curriculum Vitae}

\thispagestyle{empty}

\section{Contact information}

	Department of Spatial Sciences \\
	Czech University of Life Sciences in Prague \\
	Kamycka 129, 16500 Praha - Suchdol\\
    	E-mail: \email{grattarola@fzp.czu.cz}\\
    	Web: \href{https://flograttarola.com}{flograttarola.com}\\
    	Phone: (+420) 774 975 962‬
	ORCID: \href{https://orcid.org/0000-0001-8282-5732}{0000-0001-8282-5732}\\ 

\HRule

\section{Education}

\begin{innerlist}

\item[]{\bf  Ph.D., Life Sciences}
\hfill {2017--2021} \\
Evolution and Ecology Research Group, School of Life Sciences, {\bf University of Lincoln}, United Kingdom. Dissertation: \textit{Biodiversity informatics and macroecological patterns of biodiversity: Uruguay as a model region}. Advisor: \href{http://selectiondynamics.weebly.com/daniel-pincheira-donoso.html}{Daniel Pincheira-Donoso}.\\

\item[]{\bf  M.Sc., Biological Sciences (Genetics)}
\hfill {2013--2015} \\
Department of Biodiversity and Genetics, Clemente Estable Biological Research Institute. School of Science, {\bf Universidad de la Rep\'{u}blica}, Montevideo, Uruguay. Dissertation: \textit{Contributions of molecular ecology
to the study of mammals in Uruguay}. Advisors: \href{https://scholar.google.com.uy/citations?user=FSrtqaMAAAAJ&hl=en}{Susana González} and \href{https://scholar.google.com/citations?user=uWh1ONQAAAAJ&hl=es}{Mariana Cosse}.\\

\item[]{\bf  B.Sc. (Hons), Biological Sciences}
\hfill {2006--2012} \\
School of Science, {\bf Universidad de la Rep\'{u}blica}, Montevideo, Uruguay. Advisor: \href{https://scholar.google.com/citations?user=uWh1ONQAAAAJ&hl=es}{Mariana Cosse}.\\

\end{innerlist}

\HRule

\section{Professional experience}

\begin{innerlist}

\item[]{\bf Postdoc}
\hfill {Apr. 2021--present} \\
Department of Spatial Sciences, {\bf Czech University of Life Sciences}, Prague, Czech Republic.\\

\item[]{\bf Intern}
\hfill {Jan. 2021 -- Apr. 2021} \\
Knowledge Management, Conserving Land and Seascapes Team, {\bf UN Environmental Programme - World Conservation Monitoring Centre}, Cambridge, UK.\\

\item[]{\bf Demonstrator}
\hfill {Aug. 2018 -- Dec. 2020} \\
School of Life Sciences, {\bf University of Lincoln}, Lincoln, UK.\\

\item[]{\bf Project Manager}
\hfill {Jun. 2017 -- Jul. 2017} \\
Vida Silvestre Uruguay NGO, Montevideo, Uruguay.\\

\item[]{\bf Research Assistant}
\hfill {Nov. 2016 -- Mar. 2017} \\
Department of Animal Genetics, School of Veterinary, {\bf Universidad de la Rep\'{u}blica}, Montevideo, Uruguay.\\

\item[]{\bf Field Assistant}
\hfill {Oct. 2016 -- Nov. 2016 } \\
Project Rural Futures, {\bf Technische Universität Berlin}, Uruguay.\\

\item[]{\bf Lab Technician}
\hfill {Nov. 2015 -- Oct. 2016}\\
Department of Genetics, {\bf Rural Association of Uruguay}, Montevideo, Uruguay.\\

\item[]{\bf Research Assistant}
\hfill {Nov. 2015 -- Oct. 2016}\\
Institute of Hygiene, School of Medicine, {\bf Universidad de la Rep\'{u}blica}, Montevideo, Uruguay. Bioinformatics of Salmonella\\

\item[]{\bf Research Assistant}
\hfill {2012--2015}\\
Department of Biodiversity and Genetics, {\bf Clemente Estable Biological Research Institute}, Montevideo, Uruguay.\\

\item[]{\bf Teaching Assistant}
\hfill {2012--2014}\\
Extension Unit, School of Science, {\bf Universidad de la Rep\'{u}blica}, Montevideo, Uruguay.\\\\\\

\end{innerlist}


\HRule

\section{Peer-reviewed articles}

\begin{etaremune}

\item Pincheira-Donoso D., Harvey L.P., \underline{Grattarola F.}, Winter M., Jara M., Cotter S.C., Tregenza T. \& Hodgson D.J. (2021) The multiple origins of sexual size dimorphism in global amphibians. \textit{\textbf{Global Ecology and Biogeography}}, 30(2): 443-458. [\href{https://doi.org/10.1111/geb.13230}{link}]

\item \underline{Grattarola F.}, Martínez-Lanfranco, J.A., ... \& Pincheira-Donoso D. (2020) Multiple forms of hotspots of tetrapod biodiversity and the challenges of open-access data scarcity. \textit{\textbf{Scientific Reports}}, 10(1): 1-15. [\href{https://doi.org/10.1038/s41598-020-79074-8}{link}]

\item \underline{Grattarola F.}, Mai, P., ... \& Pincheira-Donoso D. (2020) Biodiversidata: A novel dataset for the vascular plant species diversity in Uruguay. \textit{\textbf{Biodiversity Data Journal}}, 8: e56850. [\href{https://doi.org/10.3897/BDJ.8.e56850}{link}]

\item \underline{Grattarola F.} \& Rodríguez-Tricot L. (2020) Mammals of Paso Centurión, an area with relicts of Atlantic Forest in Uruguay. \textit{\textbf{Neotropical Biology and Conservation}}, 15(3): 267–283. [\href{https://doi.org/10.3897/neotropical.15.e53062}{link}]

\item D’Alessandro B., Pérez Escanda V., Balestrazzi V., \underline{Grattarola F.}, ... \& Betancor L.  (2020) Comparative genomics of Salmonella enterica serovar Enteritidis ST-11 isolated in Uruguay reveals lineages associated with particular epidemiological traits. \textit{\textbf{Scientific Reports}}, 10: 3638. [\href{https://doi.org/10.1038/s41598-020-60502-8}{link}]

\item \underline{Grattarola F.}, Botto, G., ... \& Pincheira-Donoso D. (2019) Biodiversidata: an open-access biodiversity database for Uruguay. \textit{\textbf{Biodiversity Data Journal}}, 7: e36226. [\href{https://doi.org/10.3897/BDJ.7.e36226}{link}]

\item \underline{Grattarola F.} \& Pincheira-Donoso D. (2019) Data-sharing in Uruguay, the vision of collectors and data users. \textit{\textbf{Boletín de la Sociedad Zoológica del Uruguay}}, 28(1): 1-14. [\href{https://doi.org/10.26462/28.1.1}{link}]

\item Bergós L., \underline{Grattarola F.}, Barreneche J.M., Herández D., \& González S. (2018) Fogones de Fauna: an experience of participatory monitoring of wildlife in rural Uruguay. \textit{\textbf{Society \& Animals}}, 26(2), 171-185. [\href{https://doi.org/10.1163/15685306-12341497}{link}]

\item Chouhy M., Santos C., Gaucher L., \underline{Grattarola F.}, ... \& Perazza, G. (2017) At the frontiers of knowledge: the quest for an integral training course on society-nature. \textit{\textbf{Integralidad Sobre Ruedas}}, 4(1): 62–77. [\href{https://ojs.fhce.edu.uy/index.php/insoru/article/view/234}{link}]

\item Cosse M., \underline{Grattarola F.}  \& Mannise N. (2017) A novel real-time TaqMan\texttrademark PCR assay for simultaneous detection of Neotropical fox species using noninvasive samples based on cytochrome C oxidase subunit II. \textit{\textbf{Mammal Research}}, 62(4): 405-411. [\href{https://doi.org/10.1007/s13364-017-0328-y}{link}]

\item \underline{Grattarola F.}, Hernández D., ... \& Rodríguez-Tricot R. (2016) First record of jaguarundi (Puma yagouaroundi) (Mammalia: Carnivora: Felidae) in Uruguay,with comments about  participatory monitoring. \textit{\textbf{Boletín de la Sociedad Zoológica del Uruguay}}, 25(1): 85-91. [\href{http://szu.org.uy/journal/index.php/Bol_SZU/article/view/23}{link}]

\item \underline{Grattarola F.}, Cosse M. \& González S. (2015) A novel primer set for mammal species identification from feces samples. \textit{\textbf{Conservation Genetic Resources}}, 7: 57–59. [\href{https://doi.org/10.1007/s12686-014-0359-5}{link}]

\end{etaremune}

\HRule

\section{Service for Journals}

{\bf Reviewer for}: \textit{Biodiversity Data Journal, Global Ecology and Biogeography, Journal of Biogeography}

\HRule

%\newpage
\section{Citation \\ Metrics}

Accessed 11 Mar 2022:

\begin{itemize}
\item \textbf{Google Scholar:} 67 citations, h-index  = 5.

\end{itemize}

\HRule

\section{Students}

\begin{innerlist}

\item[]{\bf Enzo Cavalli}, BSc (Honours) in Biological Sciences, School of Science, {\bf Universidad de la Rep\'{u}blica} (Advisor, finished in 2019)

\end{innerlist}

\HRule

\section{Lecturing}

\begin{innerlist}

\item[]{\bf Modern Mammals} - Universidad de la Rep\'{u}blica, Uruguay
\hfill {2017-2019}\\
Lecture in the graduate course of Palaeontology, for 15-20 students. Invited by Dr. Richard Fari\~{n}a. 
[\href{https://flograttarola.com/pdf/mamiferos_julana.pdf}{link to slides}]

\medskip

\item[]{\bf Management and analysis of camera trap records using R software} - Ministry of Environment, Uruguay
\hfill {2018}\\
Course for NGOs, researchers and government people. Taught together with Juan M. Barreneche and Gabriel Perazza.
[\href{https://github.com/bienflorencia/curso_camtrapR}{link to syllabus}]

\medskip

\item[]{\bf Introduction to Python} - Universidad de la Rep\'{u}blica, Uruguay
\hfill {2016--2017}\\
Lecture at posgraduate course of Introduction to command line and programming for bioinformatic analysis, for 25-30 students in Biological Sciences. Invited by Dr. Andr\'{i}s Iriarte. 
[\href{https://github.com/bienflorencia/clases_python}{link to syllabus}]

\medskip

\item[]{\bf Society \& Nature} - Universidad de la Rep\'{u}blica, Uruguay
\hfill {2016--2017}\\
Graduate course for ca. 20 students of Anthropology, Biology, Geography and Social Sciences. Taught together with Carlos Santos, Javier Taks, Magdalena Chouhy, Andrea Garay, Luc\'{i}a Berg\'{o}s and Gabriel Perazza.
[\href{https://udelar.edu.uy/retema/actividades/grupos-de-trabajo/}{link to S\&N Group}]

\end{innerlist}

\HRule

\section{Grants, funding}

\begin{innerlist}

\item[]{\bf NatGeo Explorer}
\hfill {2021--2022} \\
1-year grant, 'NaturalistaUY: the iNaturalista community in Uruguay'. National Geographic Society, United States.
\\

\item[]{\bf Ph.D. International Fellowship}
\hfill {2017--2020} \\
3-year grant at the Univeristy of Lincoln, Lincoln, UK. National Agency for Research and Innovation (ANII) Uruguay POS\_EXT\_2016\_1\_136663
\\

\item[]{\bf Post-graduate National Fellowship}
\hfill {2013--2015} \\
2-year grant at the Universidad de la Rep\'{u}blica, Montevideo, Uruguay. National Agency for Research and Innovation (ANII) Uruguay POS\_NAC\_2012\_1\_8976
\\

\item[]{\bf Internship for Post-graduate Students}
\hfill {2015} \\
3-month at the Universidad Federal de Minas Gerais, Belo Horizonte, Brazil. Association of Universities of the Montevideo Group (AUGM) Uruguay
\\

\item[]{\bf Internship for Post-graduate Students}
\hfill {2013} \\
1-month at the Mississippi State University, Starkville, United States. PEDECIBA, Uruguay
\\

\item[]{\bf Undergraduate Fellowship.}
\hfill {2010--2011} \\
1-year grant at the Universidad de la Rep\'{u}blica, Montevideo, Uruguay. National Agency for Research and Innovation (ANII) Uruguay BE\_INI\_2010\_1961
\\

\end{innerlist}

\HRule

\section{Skills}

{\bf Software}: R, Python, Windows, Linux, Bash, ArcGIS, QGIS, JAGS, HTML, CSS, SQL, Markdown, Hugo-R, jekyll, WordPress, GBIF IPT, DarwinCore standard, InkScape and Adobe suites.

\medskip

{\bf Lab}: DNA extraction, PCR, RT-PCR, Taqman probe, analysis of mitochondrial, nuclear and hypervariable markers (microsatellites and SNPs), population genetics, landscape genetics and phylogenetics, NGS sequencing (Illumina and IonTorrent), alignment, annotation, comparative genomics.

\medskip

{\bf Field}: non-invasive wildlife monitoring, camera-traps, bat sensor EchoMeter, AudioMoth acoustic logger, mammal track identification.

\medskip

{\bf Statistics}: GLM, hierarchical (mixed-effects) models, machine learning, Bayesian inference, data visualization.

\medskip

{\bf Languages}: English; Portuguese (excellent); Spanish (native).

\HRule

\section{References}


Dr. \textbf{Petr Keil}, Czech University of Life Sciences, Czech Republic. \phone +420 776 371 840. \email{keil@fzp.czu.cz}

\medskip

Dr. \textbf{Daniel Pincheira-Donoso}, Queen’s University Belfast, UK. \phone +44(0) 28 9097 2967. \email{d.pincheira-donoso@qub.ac.uk}
\medskip

Dr. \textbf{Lauren Weatherdon}, UN Environment Programme World Conservation Monitoring Centre, UK. \phone +44(0) 12 2327 7314. \email{lauren.weatherdon@unep-wcmc.org}

\medskip

Prof. \textbf{Susana González}, Clemente Estable Biological Research Institute, Uruguay. \phone +598 24861417.
\email{sugonza9@yahoo.com}



\end{document}\grid
\grid
